SIR Model with Testing and Isolation Mechanisms

### 2020-11-10 note/SIR_notes.Rnw
bib cleanup, spelling, etc

\subsection{model and parameters}
\begin{itemize}
\item $\Lambda$: force of infection defined as $$\Lambda=\beta \frac{(I_u+\eta_w I_n+\eta_w I_p+ \eta_t I_t)}{N_0},$$ where $\beta$ is transmission rate, $\eta_w$ and $\eta_t$ are the isolation parameters for awaiting and reported individuals, respectively. We assume that $\eta_t<\eta_w$, i.e., the awaiting individuals for test results have a higher transmission probability than the reported individuals.
\item $\omega$: the rate of *onward flow* from the awaiting positive compartment, $p$, to reported/tested compartment, $\rho$, or from awaiting negative compartment, $n$, back to $u$.  It has units of $1/time$.
\item $\gamma$: recovery rate ($1/time$).
\item $\rho$: per capita testing intensity across the whole population ($1/time$).
\item $W$: weighted number of people available for tests, defined as $W = W_S S_u + W_I I_u + W_R R_u$.
\item $\sigma$: scaling parameter for testing defined as $\sigma = \frac{\rho N_0}{W}$.
\item $F_Z$: Weighted testing rate defined as $F_Z=\sigma W_Z$. That is, $F_S = \sigma W_S$, $F_I=\sigma W_I$ and $F_R = \sigma W_R$.
\end{itemize}

@@

\citep{rice2020effect} Effect of school closures on mortality. Reproduce Report 9 results by spatial agent based CovidSim. 
% %%%%%%%
\subsection{Models of repeated random testing of isolated populations}
\cite{bergstrom2020frequency}
(1) Model, assumptions: They developed a function, namely expected expoisour $E(C,\tau)$, to approximate trade-offs between the frequency of testing, n, the sensitivity of testing, q, and the delay between
testing and results, d. This function is explicitly derived and was connected the effective reproduction number $R=R_0 S$, where $S$ is the proportion of population susciptable.
assumption that transmission rates are a step function: individuals who
have COVID go from non-infectious to fully infectious instantaneously,
and remain fully infectious until they are no longer able to transmit disease. Test sensitivity takes the same form over the course of infection.
More sophisticated models could allow varying infectiousness and varying
sensitivity over time, as in 
\citep{larremore2020test}.

@@

% %%%%%%%
\subsection{Other maybe-related works}
\citep{arino2020simple} developed a SLIAR compartmental model to study the spread of an epidemic, specifically COVID-19, in a population. The model incorporates an Erlang distribution of times of sojourn inincubating, symptomatically and asymptomatically infectious compartments. Basic reproduction number is derived. Also, sensitivity analysis with respect to the underlying parameters for the following two outputs was carried out; (i) the number of observable cases during the course of the epidemic and at the peak, and (ii) the timing of the peak of the outbreak. Sensitivity analysis is performed using the R package multisensi.

>>>>

\subsection{model and parameters}
\begin{itemize}
\item $\Lambda$: force of infection defined as $$\Lambda=\beta \frac{(I_u+\eta_w I_n+\eta_w I_p+ \eta_t I_t)}{N_0},$$ where $\beta$ is transmission rate, $\eta_w$ and $\eta_t$ are the isolation parameters for awaiting and reported individuals, respectively. We assume that $\eta_t<\eta_w$, i.e., the awaiting individuals for test results have a higher transmission probability than the reported individuals.
\item $\omega$: the rate of *onward flow* from the awaiting positive compartment, $p$, to reported/tested compartment, $\rho$, or from awaiting negative compartment, $n$, back to $u$.  It has units of 1/time.
\item $\gamma$: recovery rate (1/time).
\item $\rho$: per capita testing intensity across the whole population (1/time).
\item $W$: weighted number of people available for tests, defined as $W = W_S S_u + W_I I_u + W_R R_u$.
\item $\sigma$: scaling parameter for testing defined as $\sigma = \frac{\rho N_0}{W}$.
\item $F_Z$: Weighted testing rate defined as $F_Z=\sigma W_Z$. That is, $F_S = \sigma W_S$, $F_I=\sigma W_I$ and $F_R = \sigma W_R$.
\end{itemize}

@@

\citep{rice2020effect} Effect of school closures on mortality. Reproduce Report 9 results by spatial agent based CovidSim. 
% %%%%%%%
\subsection{Models of repeated random testing of isolated populations}
\cite{bergstrom2020frequency}
(1) Model, assumptions: They developed a function, namely expected exposure $E(C,\tau)$, to approximate trade-offs between the frequency of testing, n, the sensitivity of testing, q, and the delay between
testing and results, d. This function is explicitly derived and was connected the effective reproduction number $R=R_0 S$, where $S$ is the proportion of population susceptible.
assumption that transmission rates are a step function: individuals who
have COVID go from non-infectious to fully infectious instantaneously,
and remain fully infectious until they are no longer able to transmit disease. Test sensitivity takes the same form over the course of infection.
More sophisticated models could allow varying infectiousness and varying
sensitivity over time, as in 
\citep{larremore2020test}.

@@

% %%%%%%%
\subsection{Other maybe-related works}
\citep{arino2020simple} developed a SLIAR compartmental model to study the spread of an epidemic, specifically COVID-19, in a population. The model incorporates an Erlang distribution of times of sojourn in incubating, symptomatically and asymptomatically infectious compartments. Basic reproduction number is derived. Also, sensitivity analysis with respect to the underlying parameters for the following two outputs was carried out; (i) the number of observable cases during the course of the epidemic and at the peak, and (ii) the timing of the peak of the outbreak. Sensitivity analysis is performed using the R package multisensi.
